A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-12-10 archive/v3/docs/discussion_v3.02.tex
Continued rewriting discussion (merger).

%==============
\begin{figure}
\centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
  \label{fig:vcirc_comparison}
\end{figure}
%==============

@@

Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip. It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}). It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).

>>>>

%==============
\begin{figure}
\centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW} and Figure \ref{fig:modelB4_models} (green). (b) Lens model from Section \ref{sec:results_lensing} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line). (c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).  (d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines). \Wilma{[TO DO: In Plot, change symbol for M/L einstein and use full number. Mass follows light curve orange. Dutton blue.]}}
  \label{fig:vcirc_comparison}
\end{figure}
%==============

@@

Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip. It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}). It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).e
